Let’s Disco – Publishing person-level data as Linked Data.

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
ESWC 2015 Tutorial

Thomas Bosch and Benjamin Zapilko hold a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London [1].
We got great feedback for this tutorial and had the idea to provide this tutorial at the ESWC conference next year as well.

@@

>>>>

Thomas Bosch and Benjamin Zapilko hold a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
We got great feedback for this tutorial and had the idea to provide this tutorial at the ESWC conference as well.
At the EDDI conference, we reached the first part of our audience - data professionals and the DDI community.
At the ESWC conference, we want to reach the second part of our audience - Linked Data experts.

@@

%short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)

Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} (M.Sc. in Computer Science) is a PhD student at Gesis - Leibniz Institute for the Social Sciences in Mannheim , Germany since 2010.
He studied Information Systems at the Technical University of Munich.
His general research topic is about RDF validation. 
He hold multiple conference and workshop presentations (e.g. ISWC, DC, WWW, Dagstuhl seminars) in the last five years.
